Generalized Plackett-Luce Likelihoods

### 2022-08-15 inst/jss_hyper3.Rnw
typos

Thus the winner was $a$, second place for $b$, third for $a$, and so
on.  Alternatively we might say that $a$ came first, fourth, and
fifth; $b$ came third and sixth, and $c$ came second.  The
Plackett-Luce likelihood function for $p_a,p_b,p_c$ would be

@@

Above, object \code{L} is an object of class \code{hyper3}; it may be
evaluated at points in probability space [that is, a vector
\code{[a,b,c]} of nonnegative values with unit sum] using standard
\proglang{R} idiom wrapping \proglang{C++} back end.

The package includes an \proglang{S4} class \code{hyper3} for this
type of object.  Package idiom for creating such objects uses named
vectors:

@@

We may find a maximum likelihood estimate for the players' strengths:

>>>>

Thus the winner was $a$, second place for $c$, third for $b$, and so
on.  Alternatively we might say that $a$ came first, fourth, and
fifth; $b$ came third and sixth, and $c$ came second.  The
Plackett-Luce likelihood function for $p_a,p_b,p_c$ would be

@@

Above, object \code{L} is an object of class \code{hyper3}; it may be
evaluated at points in probability space [that is, a vector
\code{[a,b,c]} of nonnegative values with unit sum] using standard
\proglang{R} idiom wrapping \proglang{C++} back end.  The package
includes an \proglang{S3} class \code{hyper3} for this type of object.
Package idiom for creating such objects uses named vectors:

@@

We may find a maximum likelihood estimate for the players' strengths,
using generic function \code{maxp()}:
